Geometric Control for Autonomous Landing on Asteroids

### 2017-08-08 manuscript.tex
Start on adding ORB slam summary

We implement a form of visual odometry to estimate the attitude and position of the spacecraft from a series of moncular imagery.

>>>>

We seek to utilize well-proven methods in the computer vision and robotics community to first localize the position of the spacecraft from visual imagery.
A secondary step, which is left to a subsequent publication, is then to use this imagery to autonomously update the position of the spacecraft while simultaneously mapping the surface. 
We utilize the state of the art ORB-SLAM implementation to estimate the state of the spacecraft using monocular images~\cite{mur-artal2015}.
